---
title: "Homework 1"
author: "Ghislaine Jumonville"
date: 2023-09-14
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

## Problem 1

```{r loading in early_january_weather}
library(moderndive)
data("early_january_weather")
```

In the dataset `early_january-weather`, there are `r nrow(early_january_weather)` observations that represent hourly measurements and `r ncol(early_january_weather)` variables : 

* `origin`: weather station
* `year`, `month`, `day`, `hour`: time of recording 
* `temp`, `dewp`: temperature and dew point (Fahrenheit)
* `humid`: relative humidity
* `wind_dir`, `wind_speed`, `wind_gust`: wind direction (in degrees), wind speed and gust speed (in mph)
* `precp`: precipitation (in inches)
* `pressure`: sea level pressure (in millibars)
* `visib`: visibility (in miles)
* `time_hour`: date and hour of recording as a `POSIXct` date

The mean temperature (in Fahrenheit) is `r mean(pull(early_january_weather,temp))` Fahrenheit.

The chunk below creates a scatterplot with `time_hour` on the x-axis and `temp` on the y-axis. The colors of the dots correspond to the humidity (`humid`).
```{r making a scatterplot}
temp_time_plot <- ggplot(data = early_january_weather, 
                         aes( x = time_hour, y = temp, color = humid)) + 
                  geom_point() +
                  labs(y= "Temperature (in Fahrenheit)", x = "Hourly Temperature and Date")
print(temp_time_plot + labs(title = "Early January Temperature and Relative Humidity",
                            colour = "Relative Humidity"))
ggsave("temp_time_plot.png")
```

Looking at the scatter plot, the temperature fluctuates throughout the day as there is an oscillating pattern; however, the overall trend of the plot shows that there is a positive linear relationship between temperature and date. It appears to be getting warmer on average as January progresses. It also appears that low temperatures are typically associated with lower relative humidity and as the month progresses and the temperature rises, so does the relative humidity.


## Problem 2

The code chunk below creates a data frame containing a sample size of 10 from a standard Normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 10, and a factor vector of length 10 with 3 different factor "levels".

```{r}
hw1_q2_df <- tibble(
    norm_sample = rnorm(10),
    logic_vec = norm_sample > 0,
    char_vec = c(length = 10),
    fac_vec = factor(x = c(10), levels = 3)
)

hw1_q2_df

```

